# A Common Body of Knowledge {#bok}

```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 350, message = F, comment = F, warning = F)
```

As a foundation for this effort, MDHHS has begun to develop a shared repository of key terms and concepts, their definitions, and how these are related to one another.  This common language has the following key features:

- Relates all terminology back to the person, who drives service delivery
- Includes concepts related to person-centered practices, as broadly defined above, as well as common attributes for understanding the person^[Note that the body of knowledge is not intended to classify services and supports.]
- Promotes consistency in implementation and training, and a platform for future development.
- Allows for change; the language can be extended as new concepts are identified.^[This approach also requires that ideas claiming to be new must differentiate themselves from existing terms and concepts.]
- Reduces confusion across various policies with inconsistent terminology and scope

## What is a Body of Knowledge?

> "If you wish to converse... define your terms."
>
> --- Voltaire

Person-centered thinking and planning should never become rote, and continue to be a part of a living dialogue.  Dialogue and consistent implementation require a shared language.^[According to Will Durant, this requirement is "the heart and soul of [logic], that every important term... be subjected to strictest scrutiny and definition. It is difficult, and ruthlessly tests the mind; but once done it is half of any task." @durant]  

Our purpose here is to identify and define concepts related to person-centered planning.  This is done in a way which connects core concepts to both state and federal regulations.  This collection of core concepts is intended to serve as an evolving, foundational outline for a body of knowledge; encompassing person-centered thinking, planning, implementation and monitoring.^[Please note that the current work aims at an initial proof-of-concept, and not as a process ready for automation or scaling.]

## Potential Uses

Potential uses of this body of knowledge include the following:

- *Policy Search*: searching of existing policies in electronic format to identify requirements related to each core concept of person-centered practice.
- *Impact of Policy Changes*: identification of relevant new federal policy requirements to allow for clear understanding of which current policies are related and complicated by the new federal policy
- *Basis of Curriculum*: serving as the foundation of [a standard curriculum](#curriculum) to train people receiving services, their families, direct-care team members, supports coordinators, case managers, clinicians, and others about the PCP process.
- *Monitoring Quality*: allowing for [system-level monitoring of the quality of PCP practice](#measure), through measurements and/or the use of a best practice review model.^[This could be developed similar to the MI-FAST model, which has been used to review the fidelity to evidence-based practices.]
- *Promising Practices*: use of key terms for ongoing literature review and meta-analysis of PCP-related practices in the research literature, to build [a base of best practices and evidence for effectiveness](#research).

## Identifying Core Concepts

### What makes a concept a 'core' concept?

```{r}
concept_summary <-
  concepts %>%
  filter(!is.na(concept)) %>%
  group_by(concept) %>%
  summarize(
    includes = paste(term,collapse = "; "),
    n_terms = n_distinct(term),
    n = sum(term_count)
  ) %>%
  arrange(desc(n))
```

In order to compile relevant policies and guidance related to person-centered practice, we selected and defined an initial set of core concepts related to person-centered planning.  The 'source of truth' for these concepts is defined with greater detail [in the following section](#policy_scope).

The following methods were used to develop this initial set of core concepts:
<!-- Add appendix regarding detailed methods.  Produce core datasets using scripts in regulate repo and load at beginning. -->

- **Manual review and synopsis** of key documents which define person-centered planning in the Michigan Public Behavioral Health System.  These include (a) the Person-Centered Planning Policy^[@pcp-policy], (b) the Self-Direction Technical Requirement Guide^[@sd-policy], and (c) the Michigan Mental Health Code section 330.1712 Individualized written plan of services^[@mi-mhc].
- **Automatic key phrase identification** from all source documents to identify significant phrases.
- **Identifying synonyms** across identified terms and phrases. For instance, the term *person* was mapped to terms such as *patient*, *recipient*, and *beneficiary*.  This was done for terms and phrases in order to identify their occurrence across multiple policies.
- **Purposeful Word Choice.**  We select a distinct, 'master' term to refer to various synonyms across documents. The selection of terms is informed by a consistent set of principles.
- **Annotation** for source documents, to identify the presence and concentration of each core concept in each page/section.

```{r plot_concept, fig.height=5, fig.width=6}
concept_summary %>% 
  ggplot(
    aes(
      x = fct_reorder(str_replace_all(concept,"_"," "),n), 
      y = n
    )
  ) +
  geom_col() +
  labs(
    title = "Person-Centered Planning Concepts",
    subtitle = "Most frequent concepts found in state and federal policies",
    x = "Concept", y = "Occurrences"
  ) +
  coord_flip() +
  theme_doc_flip
```

If additional concepts are identified, these can be added to the document tagging in order to associate particular regulations with these concepts.

### Characteristics of a Person  

To honor the person in the language used, and to do so simply, we define each person as having the following features:

- **description**: a set of characteristics specific to the person, defined by that person and those who know the person well.
- **connections**: the people, places and things which make up the context of a person's life
- **direction**: what the person intends for his/her life to become, by imagining a future and making choices to move toward it

Note that these are features of being human for all of us.  The intent of this framework is to describe attributes of a person which are more broadly human, and not merely focused on illness or disability.  Each person has dignity and is worthy of respect, and must be treated this way by those who provide services and supports.  

While this framework is intended for implementation with Medicaid public behavioral health recipients, the approach outlined here should apply to any reader: from legislators to clinicians, from administrators and direct-care workers.

```{r, fig.width=6,fig.height=7, dpi=300}
library(tidygraph); library(ggraph)

x <- 
  as_tbl_graph(pcp_edges) %>% 
  activate(nodes) %>% 
  left_join(pcp_nodes, by = c("name" = "concept_name")) %>%
  left_join(concept_summary, by = c("name" = "concept")) %>%
  mutate(
    root = node_is_root(),
    n = ifelse(!is.na(n),n,0),
    n_terms = ifelse(!is.na(n_terms),n_terms,0)
  ) %>%
  select(-synonyms,-definition_source)

ggraph(x, layout = "dendrogram",circular = T) +
  geom_edge_elbow(alpha = 0.5, color = "grey") +
  geom_node_point(aes(color = n,size = n_terms),show.legend = F) +
  geom_node_text(
    aes(label = name), #family = "Arial Narrow",
    repel = T, nudge_y = 0.01
  ) +
  labs(
    title = "Elements of Person-Centered Planning",
    subtitle = "Note that person is at center, not process..."
  ) +
  theme_graph()
```


```{r viz, include=FALSE}
library(visNetwork)
tst <-
  x %>%
  activate(nodes) %>%
  rename(title = concept_definition) %>%
  mutate(value = log(n + 1)) %>%
  toVisNetworkData()

p <-
  visNetwork(
    nodes = tst$nodes, 
    edges = tst$edges
  ) %>% 
  visOptions(
    highlightNearest = T
  ) %>%
  visHierarchicalLayout(
    # direction = "LR",
    sortMethod = "directed"
  )

visSave(p,"pcp_network.html")
x %>% activate(nodes) %>% as_tibble() %>% write_csv("data/concept_descriptions.csv")

```


Each element of the person-centered planning framework is shown above.  Each concept is defined by its relation with other concepts, as well as having a distinct definition, as shown below.

<!-- Add concluding description and notes regarding graph viz -->

## Defining Core Concepts {#define}

Defining core concepts and terms, using policy where possible.

```{r}
pcp_nodes %>%
  select(concept_name,concept_definition,synonyms) %>%
  filter(!is.na(concept_definition)) %>%
  knitr::kable(
    col.names = c("Concept","Definition","Synonyms"),
    caption = 'Concept Definitions and Synonyms'
  )
```


<!-- Output table from concept map -->
