# Comprehensive Mapping to Policy {#policy}

As with any important idea, person-centered planning has been discussed and debated for decades, leaving a vast body of policy, regulations, guidance, and explanations to sift through.  While the basic idea of person-centered planning is simple and commonsense, practitioners are also required to adhere to complex existing policies. With this in mind, the body of knowledge is being developed:

- Based on a broad scope of relevant state and federal policies identified by MDHHS-BHDDA.
- Using natural-language processing techniques to identify and refine core terminology from the text of the identified policies
- In a manner that allows MDHHS-BHDDA to identify whether new federal policies would align with the current implementation of PCP

## Identify Scope of Policy {#policy_scope}

In collaboration with policy experts at MDHHS-BHDDA, we identified the following initial scope of state and federal regulations:

1. *MDHHS BHDDA Policy & Practice Guidelines*: All documents posted on the [MDHHS list of policy and practice guidelines](https://www.michigan.gov/mdhhs/0,5885,7-339-71550_2941_4868_4900---,00.html).  These include the Person-Centered Planning Policy^[@pcp-policy] and the Self-Direction Technical Requirement Guide^[@sd-policy].
2. *Michigan Medicaid Provider Manual*: The manual contains coverage, billing, and reimbursement policies for Medicaid, Healthy Michigan Plan, Children's Special Health Care Services, Maternity Outpatient Medical Services (MOMS), and other healthcare programs administered by the Michigan Department of Health and Human Services (MDHHS).
3. *Michigan Mental Health Code*: The Michigan Mental Health Code section 330.1712 regarding the individualized written plan of services^[@mi-mhc].
4. *SAMHSA CCBHC Criteria*: The formal certification criteria for Certified Community Behavioral Health Clinics, which contains person-centered planning as a component of the program model^[@ccbhc_criteria].
5. *PIHP Contract Bundle*: The current bundle of contracts for Prepaid Inpatient Health Plans in Michigan.
6. *LARA Licensing Rules and Statutes*: [All posted licensing rules](https://www.michigan.gov/lara/0,4601,7-154-89334_63294_27717_67459_67461-327086--,00.html) for Adult Foster Care and Home for the Aged facilities, which have overlapping requirements related to individual planning.  These include the Adult Foster Care Act (PA 218 of 1979) and the Public Health Code (PA 368 of 1978).
7. *Federal Medicaid Rules*: All final rule documents from the Centers for Medicaid and Medicare Services (CMS) containing the phrases 'person-centered', 'self-determination', and/or 'plan of care'.  These were filtered to exclude policies which applied to Medicare only.  

The result is a set of `r nrow(reg_list)` regulatory documents used to identify key concepts related to person-centered practice:

```{r}

reg_list %>%
  group_by(agencies) %>%
  select(agencies,short_title) %>%
  knitr::kable(
    col.names = c("Source","Abbreviated Title"),
    caption = 'Regulations included in PCP body of knowledge.'
  )

```

This set of policies and regulations can be expanded as necessary.^[For example, by refining a query to the Federal Register API to [search for policies](https://www.federalregister.gov/documents/search?conditions%5Bagencies%5D%5B%5D=centers-for-medicare-medicaid-services&conditions%5Bagencies%5D%5B%5D=health-and-human-services-department&conditions%5Bagencies%5D%5B%5D=substance-abuse-and-mental-health-services-administration&conditions%5Bterm%5D=person-centered&conditions%5Btype%5D%5B%5D=RULE#) containing the phrase "person-centered" by relevant agencies.]  Additional work will be needed to assure that the most current version of amended policies is used, as this approach is refined.

## Find Occurrence of Concepts in Policy

The core concepts are derived from key policy documents, as defined in [the previous section](#bok), which allows for related terms to be flagged within other policy documents.  One of the most challenging issues facing any attempt to give clear, consistent, and comprehensive guidance related to person-centered planning is the large, diverse, and continually evolving set of requirements and guidance.

The previous section outlined the process for deriving key concepts from state-level policies and guidelines.  The next step is to identify these concepts when they occur within a much larger set of federal policies.  This will allow for policy specialists to:

- suggest necessary refinements to the body of knowledge
- identify relevant requirements which were previously unknown
- identify potential discrepancies between policies which address a similar concept

To do this, this analysis maps policy words and phrases with their corresponding concepts.  As new policies are identified for inclusion, new synonyms for core concepts will need to be identified if new terms are introduced to refer to existing concepts.

The plot below shows the number of occurrences^[using log scale to show the less frequently used terms] of core concepts across the entire corpus of policies identified above.  While the frequency of occurrence does not speak to the importance of one concept in relationship to others, it point out the number of uses of the concept in different contexts, underlining the challenge in harmonizing divergent policy language.

```{r policy_annotate, eval=FALSE, include=FALSE}
policy_annot <- 
  df %>%
  # filter(document %in% c("PCP","Self-D")) %>%
  mutate(doc_id = document) %>%
  # Collapse each document to a single row
  group_by(doc_id) %>%
  summarize(text = paste(text,collapse = " ")) %>%
  cleanNLP::cnlp_annotate() %>% 
  .$token 

feather::write_feather(policy_annot,"data/policy_annot.feather")
```

```{r policy_concept, cache=TRUE}
policy_annot <- feather::read_feather("data/policy_annot.feather")
policy_concepts <- policy_annot %>% flag_concepts()

sum_policy <-
  policy_concepts %>%
  # Remove punctuation, conjunctions, etc.
  filter(!upos %in% c("PUNCT","DET","CCONJ","ADP","PART","AUX")) %>%
  group_by_all() %>%
  summarize(n = n()) %>%
  filter(!is.na(concept_name)) %>% 
  group_by(concept_name,doc_id) %>% 
  summarize(n = n())
```

```{r plot_policy_concept, fig.height=7, fig.width=6.5}
library(scales)

sum_policy %>% 
  arrange(desc(n)) %>% 
  ggplot(
    aes(
      x = fct_reorder(concept_name,.x = log(n),.fun = sum), 
      y = n,
      fill = doc_id
    )
  ) +
  geom_col() +
  scale_y_log10(
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))
  ) +
  labs(
    title = "Person-Centered Planning Concepts",
    subtitle = "Most frequent concepts found in all policies",
    x = "Concept", y = "Occurrences"
  ) +
  coord_flip() +
  # scale_fill_brewer(type = "qual", palette = "Accent") +
  theme_minimal() + 
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(family = "Arial Narrow"),
    axis.text.x = element_blank()
  )
```

<!-- Note caveats and work in progress for concept mapping across federal policies -->

```{r collapsed}

collapsed <- 
  policy_concepts %>%
  mutate(
    concept_word = if_else(
      is.na(concept_name),
      token,
      paste0("{",concept_name,"}")
    )
  ) %>%
  group_by(doc_id, sid) %>%
  summarize(
    text = paste0(token, collapse = " "),
    rev_text = paste0(concept_word, collapse = " "),
    concepts_incl = paste0(concept_name, collapse = ";")
  ) %>%
  mutate(
    concepts_incl = str_replace_all(concepts_incl,"NA;|NA|;NA",""),
    concepts_incl = str_split(concepts_incl, ";")
  )

```

```{r}
x <- "assessment"
filt <- collapsed %>% filter(map_lgl(concepts_incl, ~ x %in% .))
```

An example may be helpful in understanding what goes into the chart above.  For instance, the concept of *`r x`* shown in the chart above occurs `r sum_policy %>% filter(concept_name == x) %>% summarize(n = sum(n)) %>% .$n` times across `r sum_policy %>% filter(concept_name == x) %>% summarize(docs = n_distinct(doc_id)) %>% .$docs` separate policy documents.^[The specific policies including this concept are: `r sum_policy %>% filter(concept_name == x) %>% summarize(docs = paste0(doc_id, collapse = ", ")) %>% .$docs`]

The table below shows a sample of the text from some of the policies where this concept is flagged:

```{r}

if("html_document" %in% rmarkdown::all_output_formats(knitr::current_input())[1]){
  filt %>%
    filter(doc_id %in% c("AFC-TA","MHCode","HCBS")) %>%
    select(doc_id,text,sid) %>%
    DT::datatable()
} else {
  filt %>%
    filter(doc_id %in% c("AFC-TA","MHCode","HCBS")) %>%
    select(doc_id,text,sid) %>%
    slice(1:15) %>%
    knitr::kable()  
}
```

<!-- Additional Analyses/Viz -->
<!-- frequency of terms by doc_id (small multiples) -->
<!-- which policies have relevant content for specific concepts -->
<!-- summarize the content for a specific concept across policies -->
