--- 
title: "A Person-Centered Framework"
author: "Various authors"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
description: A working document outlining the process, sources, and formation of a comprehensive body of knowledge for person-centered planning.
documentclass: book
link-citations: yes
bibliography:
- book.bib
- packages.bib
site: bookdown::bookdown_site
biblio-style: apalike
---

```{r setup, echo=FALSE, include=FALSE}
library(tidygraph); library(tidyverse); library(tidytext)
library(topicmodels); library(tm)
library(cleanNLP); cleanNLP::cnlp_init_udpipe()

#Set global opts
knitr::opts_chunk$set(echo = FALSE, dpi = 350, message = F, comment = F)

# Load datasets
corpus <- feather::read_feather("data/corpus.feather")
pcp_nodes <- readxl::read_excel("data/pcp_concept_map.xlsx",sheet = "nodes")
pcp_edges <- readxl::read_excel("data/pcp_concept_map.xlsx",sheet = "edges")

```

**This document is currently a work in progress and is not intended for distribution outside of those collaborating on its development with the direction of MDHHS-BHDDA.**

# Reason
 
This framework arises from a simple conviction: the intent of supports and services is to help each person flourish, to achieve a better life.

That belief is thankfully not a new one.  It aligns with the person-centered planning policy[@pcp-policy] published by the Michigan Department of Health and Human Services' *Behavioral Health and Developmental Disabilities Administration* (MDHHS-BHDDA), which begins by stating that:

> *The purpose of the community mental health system is to support adults and children... to live successfully in their communities — achieving community inclusion and participation, independence, and productivity [and to] to identify and achieve their personal goals.*

The framework defined below is an attempt to apply these longstanding and fundamental values in a way that allows for consistent definitions, implementation, and evaluation.

Each person has the ability to choose a better future, to chart a course toward it and strive to reach it: person-centered planning provides a platform to enable this process.  In order for services to effectively support a person in this process, they must be provided within the context of a person's goals. Orienting a broad and complex system to keep the person as its central focus requires a consistent, overarching framework.  MDHHS-BHDDA is working to support this person-centered orientation with the following strategy:

**Goal:** To develop [a common body of knowledge](#bok) for person-centered planning,
mapped to [relevant policies](#policy) and [research](#research),
which will inform a [shared curriculum](#curriculum)
and [measurement framework](#measure)
to support [improved quality of life](#pcpdca) for each person.


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
