---
title: "Identify Requirements"
params:
  concept: adjust_plan
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message = FALSE, warning = FALSE)
concept_df <- 
  read_csv("data/occurs.csv") %>% 
  filter(concept == params$concept) %>%
  filter(!is.na(snippet))
```

# Instructions

This document contains all of the regulatory language which references the concept of `r params$concept`.  Its purpose is to allow for policy experts and analysts to see the various policy snippets related to a key concept and to paraphrase the requirements of the regulation for use in fidelity

1. Read each snippet below, clicking on the link to the policy source if necessary to understand the context.
2. Highlight relevant requirement language, if that's helpful for focus.
3. Rewrite any requirements in active, concise language in the space following the `requirement:` prompt.  These should be concrete and observable requirements for use in determining implementation fidelity.
4. If the passage identifies a requirement that you have already re-written, copy/paste the text from that section after the `requirement:` prompt for the repetitive section.
5. Put any additional notes or thoughts in the `notes:` section at teh end of the document.
6. Once done, select "Save as" and save your changes to the file in the same folder by adding the prefix "rev_" to the beginning of the file name, so that a file originally named "`r paste0(params$concept,".docx")`" would be re-named "`r paste0("rev_",params$concept,".docx")`"

# Policy References

The following portions of policy pertain to the concept of *`r concept_name`*:

```{r print_it, results='asis'}
for (i in 1:nrow(concept_df)) {
  # Add some text
  cat("From the **", paste0("[",concept_df$title[i],"](",concept_df$url[i],")"), "**",  sep="")  
  cat(" beginning on page **", paste(concept_df$start_page[i]), "**",  sep="")  
  cat("  \n")  
  cat(" *", paste(concept_df$snippet[i]), "*",  sep="") 
  cat("  \n")  
  cat("  \n") 
  cat("id: ", paste(concept_df$passage_id[i]), sep="") 
  cat("  \n")  
  cat("  \n") 
  cat("requirement: ")
  cat("  \n")  
  cat("  \n")
  cat("-----")
  cat("  \n")  
  cat("  \n")

}

cat("notes: ")
cat("  \n")  
cat("  \n")
```